Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Update color

Now suppose this observer makes a measurement of the true orbit at the orange
point or the red point. Then the orange and red lines correspond to the orbits
that the observer would compute for each point. In action space, this would
correspond to a different value of $J_z$ for the orange and red points. In
this way, assuming the wrong coordinate system induces time dependence in the
actions {\em computed by an observer}.

>>>>

Now suppose this observer makes a measurement of the true orbit at the blue
point or the pink point. Then the blue and pink lines correspond to the orbits
that the observer would compute for each point. In action space, this would
correspond to a different value of $J_z$ for the blue and pink points. In this
way, assuming the wrong coordinate system induces time dependence in the
actions {\em computed by an observer}.
